Programmer friendly communication framework

### 2024-03-09 2024_paper/paper/msglink_framework.tex
started working on solution and design overview

>>>>

To solve the before mentioned problems, and implement the last missing goals, the top-level protocol in the stack (Socket.IO) will be replaced by a new protocol which has been named \textbf{msglink}.

msglink will build on top of WebSockets, implementing all features of Socket.IO that are relevant to achieve the listed goals. In addition it will add direct framework support for more commonly used communication schemes.

This section will cover the core principles of the msglink protocol and how it solves the problems and implements the goals listed above.
